---
title: "**DairyPrint Model Report**"
output:
  html_document:
    theme:
      version: 4
params:
  
  co2eq_milk: 'NULL'
  suma_table: 'NULL'
  herd_inputs: 'NULL'
  nh3_emissions: 'NULL'
  crop_inputs: 'NULL'
  co2eq_purchased: 'NULL'
  fuel_inputs: 'NULL'
  purchased_feeds: 'NULL'
  animal_data: 'NULL'
  raw_animal_df: 'NULL'
  farm_area: 'NULL'
  manure_inputs: 'NULL'
  diet_inputs: 'NULL'
  direct_storage_n2o: 'NULL'
  
  crop_n2o: 'NULL'
  crop_ammonia: 'NULL'
  crop_methane: 'NULL'
  crop_co2: 'NULL'
  
  total_ch4_emmited: 'NULL'
  total_n2o_emmited: 'NULL'
  total_co2_emmited: 'NULL'
  total_co2e_q_emitted: 'NULL'
  co2eq: 'NULL'
  plot_by_sorce: 'NULL'
  pie2_ghg_source: 'NULL'
  
  nitrogen_balance: 'NULL'
  n_purchased_feeds:  'NULL'
  nitrogen_from_bedding: 'NULL'
  nitrogen_from_fertilizers:  'NULL'
  n_fixed:  'NULL'
  nitrogen_from_barn:  'NULL'
  nitrogen_from_manure_storage:  'NULL'
  nitrogen_from_culled_cows:  'NULL'
  nitrogen_from_milk:  'NULL'
  n_leached:  'NULL'
  phosphorous_balance: 'NULL'
  p_purchased_feeds: 'NULL'
  phosphorous_from_bedding: 'NULL'
  p_from_fertilizers: 'NULL'
  phosphorous_from_milk: 'NULL'
  phosphorous_from_culled_cows: 'NULL'
  p_losses: 'NULL'
  
  
  
  potassium_balance: 'NULL'
  k_purchased_feeds: 'NULL'
  potassium_from_bedding: 'NULL'
  k_from_fertilizers: 'NULL'
  potassium_from_culled_cows: 'NULL'
  potassium_from_milk: 'NULL'
  k_losses: 'NULL'
  economics: 'NULL'
editor_options: 
  chunk_output_type: console
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 34px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 28px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 18px;
  color: #007582;
  
}
h4 { /* Header 4 */
  font-family: Helvetica;
  font-size: 14px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}
</style>

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

<div class="alert alert-info" <strong> Disclaimer: </strong> DairyPrint model is a high-level, simple, minimalistic, user-friendly,
                               still powerful, and scientifically sound whole-farm decision support
                               model to assess economic and environmental tradeoffs of dairy farming
                               for strategic nutrient management decisions.
</div>

## **1. Farm Inputs:**

## {.tabset}

### **1.1 Herd Management**

```{r, warning = FALSE, echo = FALSE, message = FALSE}
library(formattable)
library(dplyr)

kableExtra::kbl(params$herd_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = T, color = "white", background = "#007582")

```

```{r, warning = FALSE, echo = FALSE}

kableExtra::kbl(params$diet_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = T, color = "white", background = "#007582")

```

### **1.2 Manure Handling**

```{r, warning = FALSE, echo = FALSE}

manure_inputs <- params$manure_inputs 

kableExtra::kbl(manure_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = T, color = "white", background = "#007582")

```

### **1.3 Crops and Purchased Feeds**

#### **1.3.1 Crops**

```{r, warning = FALSE, echo = FALSE}

crop_inputs <- params$crop_inputs %>% 
  dplyr::select(-"crop_id") %>% 
  dplyr::rename(
    "Crop"                               = "crop_type",
    "Area"                               = "area",
    "Manure Applied (%)"                 = "manure_pct",
    "Total N Fertilizer Applied (kg/ha)" = "total_n_applied",
    "Urea Applied (% of N)"              = "urea_pct_applied",
    "Phosphate Applied (kg/ha)"          = "phosphate_applied",
    "Potash Applied (kg/ha)"             = "potash_applied",
    "Lime Applied (kg/ha)"               = "lime_applied"
  )

kableExtra::kbl(crop_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```

#### **1.3.2 Purchased Feeds**

```{r, warning = FALSE, echo = FALSE}

purchased_feeds <- params$purchased_feeds %>%
  tibble::as_tibble() %>% 
  dplyr::rename(
    "Feeds"                         = "feeds",
    "Quantitity (ton.)"             = "Qntdds",
    "Carbon Footprint (Carbon eq.)" = "carbon_foot"
  ) %>% 
  dplyr::select(-cp_content, -k_content, -p_content, -`source - co2eq`)

kableExtra::kbl(purchased_feeds, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```

### **1.4 Fuel Consumption**

```{r, warning = FALSE, echo = FALSE}

kableExtra::kbl(params$fuel_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```

## {-}

## **2. Herd** 

## {.tabset}

### **2.1 Herd inventory**

```{r, warning = FALSE, echo = FALSE,  echo = FALSE, message = FALSE}

herd_inventory <- params$animal_data %>% 
  dplyr::group_by(Categories) %>% 
  dplyr::select(Categories, total_animals) %>% 
  tidyr::pivot_wider(names_from = Categories, 
                     values_from = total_animals) %>% 
  dplyr::rename(Calves = Cal, "Lactating cows" = Cow, "Dry cows" = Dry, "Heifers" = Hei) %>% 
  dplyr::relocate("Lactating cows", "Dry cows", "Heifers", "Calves") 

herd_inventory %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```

### **2.2 Performance **

```{r, warning = FALSE, echo = FALSE,  echo = FALSE, message = FALSE}

animal_perfomance <- params$animal_data %>% 
  dplyr::select(Categories, milk_yield_kg, milk_cp_pct,  milk_fat_pct, milk_yield_kg_fpc, dmi_kg, water_l) %>% 
  dplyr::rename("Milk Yield (kg/day)"              = milk_yield_kg,
                "Milk Protein (%)"                 = milk_cp_pct,
                "Milk Fat (%)"                     = milk_fat_pct,
                "Milk Yield Cor. Fat and Prot."    = milk_yield_kg_fpc,
                "Dry Matter Intake (kg/day)"       = dmi_kg,
                "Water Intake (l/day)"             = water_l) %>% 
  dplyr::mutate_if(is.numeric, round, 1) %>% 
  tidyr::pivot_longer(cols = c("Milk Yield (kg/day)", "Milk Protein (%)",  "Milk Fat (%)", "Milk Yield Cor. Fat and Prot.", "Dry Matter Intake (kg/day)", "Water Intake (l/day)"), 
                      names_to = "values") %>% 
  tidyr::pivot_wider(names_from = Categories) %>% 
  dplyr::relocate(values, Cow, Dry, Hei, Cal) %>% 
  dplyr::rename("Variables" = values, Calves = Cal, "Lactating cows" = Cow, "Dry cows" = Dry, "Heifers" = Hei) %>%
  dplyr::select(-Calves)

animal_perfomance[3, 3] <- 0
animal_perfomance[3, 4] <- 0

animal_perfomance %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")
  
```

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

animal_data_plots <- params$raw_animal_df %>%
  tibble::as_tibble() %>%
  dplyr::filter(Categories == "Cow" & MonthSimulated == 1 & Phase %in% c("Lac1", "Lac2", "Lac3")) %>%
  dplyr::mutate(
    Phase = dplyr::if_else(Phase == "Lac1", "Primip", dplyr::if_else(Phase == "Lac2", "Second", "Multi"))
  )

plots <- list(
  y_variable = c("milk_yield_kg_cow2", "dry_matter_intake_kg_animal"),
  y_title = c("Milk Yield (kg/day)", "Dry Matter Intake (kg/day)")
) %>% 
  purrr::pmap(built_variable_over_lactation_plot, data_frame = animal_data_plots, x_variable = "Month", col_variable = "Phase")

patchwork::wrap_plots(plots[[1]], plots[[2]], ncol = 2)

```

### **2.3 Greenhouse gas emissions **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

animal_ghg_emissions <- params$animal_data %>% 
  dplyr::select(Categories, total_animals, milk_yield_kg_fpc, dmi_kg, total_manure_kg, total_ch4_kg, total_n2o_kg) %>% 
  dplyr::mutate(
    total_manure_kg = total_manure_kg / total_animals,
    total_ch4_kg = total_ch4_kg / total_animals,
    total_n2o_kg = total_n2o_kg / total_animals,
    "Methane yield (g/kg DM)" = total_ch4_kg * 1000 / dmi_kg,
    "Methane Intensity (g/kg Milk)" = total_ch4_kg * 1000 / milk_yield_kg_fpc
  ) %>% 
  dplyr::select(-total_animals, -milk_yield_kg_fpc, -dmi_kg) %>% 
  dplyr::rename("Manure excretion (kg/day)"              = total_manure_kg,
                "Enteric methane (kg/day)"               = total_ch4_kg,
                "Enteric nitrous oxide (kg/day)"         = total_n2o_kg) %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
  tidyr::pivot_longer(cols = c("Manure excretion (kg/day)", 
                               "Enteric methane (kg/day)",
                               "Enteric nitrous oxide (kg/day)",
                               "Methane yield (g/kg DM)",
                               "Methane Intensity (g/kg Milk)"), 
                      names_to = "values") %>% 
  tidyr::pivot_wider(names_from = Categories) %>% 
  dplyr::relocate(values, Cow, Dry, Hei, Cal) %>% 
  dplyr::rename("Variables" = values, Calves = Cal, "Lactating cows" = Cow, "Dry cows" = Dry, "Heifers" = Hei) %>%
  dplyr::select(-Calves)

animal_ghg_emissions[5, 3] <- 0
animal_ghg_emissions[5, 4] <- 0

animal_ghg_emissions %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

plots <- list(
  y_variable = c("fresh_manure_output_kg_day", "enteric_methane_g_animal_day"),
  y_title = c("Manure Excretion (kg/day)", "Enteric Methane (kg/day)")
) %>% 
  purrr::pmap(built_variable_over_lactation_plot, data_frame = animal_data_plots, x_variable = "Month", col_variable = "Phase")

patchwork::wrap_plots(plots[[1]], plots[[2]], ncol = 2)

```

### **2.4 Nutrient excretion **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE, fig.retina=3}

animal_nutrient_excretion <- params$animal_data %>% 
  dplyr::select(Categories, total_n_excreted_g, total_p_excreted_g, total_k_excreted_g) %>% 
  dplyr::rename("Nitrogen excretion (kg/day)"        = total_n_excreted_g,
                "Phosphorous excretion (kg/day)"     = total_p_excreted_g,
                "Potassium excretion (kg/day)"       = total_k_excreted_g) %>% 
  dplyr::mutate_if(is.numeric, \(x) x / 1000) %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
  tidyr::pivot_longer(cols = c("Nitrogen excretion (kg/day)", 
                               "Phosphorous excretion (kg/day)",
                               "Potassium excretion (kg/day)"), 
                      names_to = "values") %>% 
  tidyr::pivot_wider(names_from = Categories) %>% 
  dplyr::relocate(values, Cow, Dry, Hei, Cal) %>% 
  dplyr::rename("Variables" = values, Calves = Cal, "Lactating cows" = Cow, "Dry cows" = Dry, "Heifers" = Hei) %>%
  dplyr::select(-Calves)

animal_nutrient_excretion %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")


plots <- list(
  y_variable = c("total_nitrogen_excreted_g", "total_phosphorus_excretion_g", "total_potassium_excretion_g"),
  y_title = c("Nitrogen Excretion (kg/day)", "Phosphorous Excretion (kg/day)", "Potassium Excretion (kg/day)")
) %>% 
  purrr::pmap(built_variable_over_lactation_plot, data_frame = animal_data_plots, x_variable = "Month", col_variable = "Phase")

patchwork::wrap_plots(plots[[1]], plots[[2]], plots[[3]], ncol = 3)

```

## {-}

## **3. Manure Handling**

## {.tabset}

### **3.1 Methane **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

methane <- params$nh3_emissions %>%
  dplyr::filter(year_day > 365) 

methane %>% 
  dplyr::select(barn_ch4_emissions_kg, storage_ch4_emissions_kg) %>% 
  dplyr::summarise(
    "Total Barn Methane Emissions (Ton./Year)" = round(sum(barn_ch4_emissions_kg) / 1000, 1),
    "Total Storage Methane Emissions (Ton./Year)" = round(sum(storage_ch4_emissions_kg) / 1000, 1)
  ) %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

plots <- list(
  y_variable = c("barn_ch4_emissions_kg", "storage_ch4_emissions_kg"),
  y_title = c("Methane Emissions", "Methane Emissions"),
  plot_title = c("Barn", "Storage")
) %>% 
  purrr::pmap(built_variable_over_year_plot, data_frame = methane, x_variable = "year_day")

patchwork::wrap_plots(plots[[1]], plots[[2]], ncol = 2)

```

### **3.2 Ammonia and Nitrous Oxide **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

methane %>% 
  dplyr::select(loss_animal_kg, total_storage_N_loss) %>% 
  dplyr::summarise(
    "Total Barn Ammonia Emissions (Ton./Year)" = round(sum(loss_animal_kg) / 1000, 1),
    "Total Storage Ammonia Emissions (Ton./Year)" = round(sum(total_storage_N_loss) / 1000, 1),
    "Nitrous Oxide (Ton.Year)" = round(params$direct_storage_n2o / 1000 + `Total Storage Ammonia Emissions (Ton./Year)`/100/0.64 + `Total Barn Ammonia Emissions (Ton./Year)`/100/0.64 , 2)
  ) %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")


plots <- list(
  y_variable = c("loss_animal_kg", "total_storage_N_loss"),
  y_title = c("Ammonia Emissions", "Ammonia Emissions"),
  plot_title = c("Barn", "Storage")
) %>% 
  purrr::pmap(built_variable_over_year_plot, data_frame = methane, x_variable = "year_day")

patchwork::wrap_plots(plots[[1]], plots[[2]], ncol = 2)

```

## {-}

## **4. Purchased Feeds and Crops**

## {.tabset}

### **4.1 Methane, Ammonia, and Nitrous Oxide emissions **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE, fig.retina = 3}

tibble::tibble(
  "Variable" = c("Methane (Ton./Year)", "Ammonia (Ton./Year)", "Nitrous Oxide (Ton./Year)", "Carbon Dioxide (Ton./Year)"),
  "Values"   = c(params$crop_methane, params$crop_ammonia, params$crop_n2o, params$crop_co2)
) %>%
  dplyr::mutate_if(is.numeric, \(x) x / 1000) %>% 
  dplyr::mutate_if(is.numeric, round, 1) %>% 
  tidyr::pivot_wider(names_from = c("Variable"), values_from = "Values") %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")
  
```

## {-}

## **5. Dashboard**

## {.tabset}

### **5.1 Carbon Footprint **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

tibble::tibble(
  "Variables" = c("Total Methane (Ton./Year)", "Total Nitrous Oxide (Ton./Year)", "Carbon Dioxide (Ton./Year)", "Total CO2eq (Ton./Year)", "Carbon Footprint (Kg/kg of Milk)"),
  "Values"    = c(params$total_ch4_emmited, params$total_n2o_emmited, params$total_co2_emmited, params$total_co2e_q_emitted, params$co2eq)
) %>% 
    tidyr::pivot_wider(names_from = Variables, 
                     values_from = Values) %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")


bar_plot <- params$plot_by_sorce %>% 
  dplyr::rename("Crop/Purc. Feeds" = `Crop and purchased feeds`) %>% 
  tidyr::pivot_longer(cols = c(Herd, Barn, Manure, `Crop/Purc. Feeds`, Fuel), values_to = "Co2eq") %>% 
  ggplot2::ggplot(ggplot2::aes(x = reorder(name, -Co2eq), y = Co2eq, fill = name)) +
  ggplot2::geom_bar(stat = "identity", fill = "steelblue")+
  ggplot2::geom_text(ggplot2::aes(label = Co2eq), vjust = 1.6, color = "black", size = 3)+
  ggplot2::theme_minimal() + 
  ggplot2::ylab("Co2eq/kgMilk") + ggplot2::xlab(" ") 

data <- params$plot_by_sorce %>% 
  dplyr::rename("Crop/Purc. Feeds" = `Crop and purchased feeds`) %>%
  tidyr::pivot_longer(cols = c(Herd, Barn, Manure, `Crop/Purc. Feeds`, Fuel), values_to = "Co2eq", names_to = "Sources")

# Compute percentages
data$fraction = data$Co2eq / sum(data$Co2eq)

# Compute the cumulative percentages (top of each rectangle)
data$ymax = cumsum(data$fraction)

# Compute the bottom of each rectangle
data$ymin = c(0, head(data$ymax, n = -1))

# Compute label position
data$labelPosition <- (data$ymax + data$ymin) / 2

# Compute a good label
data$label <- paste0(data$Sources, " ", round(data$fraction * 100, 2), "\n %")

# Make the plot
pie_chart <- ggplot2::ggplot(data, ggplot2::aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = Sources)) +
  ggplot2::geom_rect() +
  ggplot2::geom_label( x = 3.5, ggplot2::aes(y = labelPosition, label = label), size = 2) +
  ggplot2::scale_fill_brewer(palette = 4) +
  ggplot2::coord_polar(theta = "y") +
  ggplot2::xlim(c(2, 4)) +
  ggplot2::theme_void() +
  ggplot2::theme(legend.position = "none")

data2 <- params$pie2_ghg_source

# Compute percentages
data2$fraction = data2$values / sum(data2$values)

# Compute the cumulative percentages (top of each rectangle)
data2$ymax = cumsum(data2$fraction)

# Compute the bottom of each rectangle
data2$ymin = c(0, head(data2$ymax, n = -1))

# Compute label position
data2$labelPosition <- (data2$ymax + data2$ymin) / 2

# Compute a good label
data2$label <- paste0(data2$ghg, " ", round(data2$fraction * 100, 1), "\n %")

# Make the plot
pie_chart2 <- ggplot2::ggplot(data2, ggplot2::aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = ghg)) +
  ggplot2::geom_rect() +
  ggplot2::geom_label( x = 3.5, ggplot2::aes(y = labelPosition, label = label), size = 2) +
  ggplot2::scale_fill_brewer(palette = 4) +
  ggplot2::coord_polar(theta = "y") +
  ggplot2::xlim(c(2, 4)) +
  ggplot2::theme_void() +
  ggplot2::theme(legend.position = "none")

patchwork::wrap_plots(bar_plot, pie_chart, pie_chart2, ncol = 3) 

```

### **5.2 Nutrient Balances **

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}
balance_n <- data.frame(
  amount =  c(params$n_purchased_feeds, params$nitrogen_from_bedding, params$nitrogen_from_fertilizers, params$n_fixed, -params$nitrogen_from_milk, -params$nitrogen_from_culled_cows, -params$nitrogen_from_barn, -params$nitrogen_from_manure_storage, -params$n_leached, params$nitrogen_balance),
  desc = c("Purchased Feeds", "Bedding", "Fertilizers", "Legumes", "Milk sold", "Culled Animals", "Barn", "Manure Storage", "Leached", "Balance")
)

balance_p <- data.frame(
  amount =  c(params$p_purchased_feeds, params$phosphorous_from_bedding, params$p_from_fertilizers,  -params$phosphorous_from_milk, -params$phosphorous_from_culled_cows, -params$p_losses, params$phosphorous_balance),
  desc = c("Purchased Feeds", "Bedding", "Fertilizers", "Milk sold", "Culled Animals", "Soil losses", "Balance")
)

balance_k <- data.frame(
  amount =  c(params$k_purchased_feeds, params$potassium_from_bedding, params$k_from_fertilizers,  -params$potassium_from_milk, -params$potassium_from_culled_cows, -params$k_losses, params$potassium_balance),
  desc = c("Purchased Feeds", "Bedding", "Fertilizers", "Milk sold", "Culled Animals", "Soil losses", "Balance")
)

total_annual_milk_yield_kg <- as.numeric(animal_perfomance[4, 2]) * 365 * herd_inventory[1, 1]

tibble::tibble(
  "Nutrient" = c("Nitrogen", "Phosphorous", "Potassium"),
  "Nutrient Balance (Ton./Year)"   = c(params$nitrogen_balance, params$phosphorous_balance, params$potassium_balance),
  "Nutrient Balance/Milk (kg/kg)"   = c(params$nitrogen_balance / total_annual_milk_yield_kg, params$phosphorous_balance / total_annual_milk_yield_kg, params$potassium_balance / total_annual_milk_yield_kg),
  "Nutrient Balance/area (kg/ha)" = c(params$nitrogen_balance * 1000 / params$farm_area, params$phosphorous_balance * 1000 / params$farm_area, params$potassium_balance * 1000 / params$farm_area)
 ) %>%
  dplyr::mutate(
    "Nutrient Balance (Ton./Year)" = round(`Nutrient Balance (Ton./Year)`, 1),
    "Nutrient Balance/Milk (kg/kg)" = round(as.numeric(`Nutrient Balance/Milk (kg/kg)`), 4),
    "Nutrient Balance/area (kg/ha)" = round(`Nutrient Balance/area (kg/ha)`, 1)
  ) %>%
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```


```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

patchwork::wrap_plots(built_waterfall_plot(balance_n, x_axis = " ", y_axis = "N (Ton./ha)"), built_waterfall_plot(balance_p, x_axis = " ", y_axis = "P (Ton./ha)"), built_waterfall_plot(balance_k, x_axis = " ", y_axis = "P (Ton./ha)"), ncol = 3)

```

### **5.3 Economics **


```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE}

params$economics %>% 
  dplyr::rename(
    "Milk Income (\\$/Cow)" = `Total Milk Income ($/cow)`,
    "IOFC Lac (\\$/Cow)"    = `Income Over Feed Cost Lac ($/cow)`,
    "IOFC Dry (\\$/Cow)"    = `Income Over feed Cost Dry ($/cow)`,
    "IOFC Lac + Dry (\\$/Cow)" = `Income Over Feed Cost Lac + Dry ($/cow)`,
    "Feed Cost (\\$/KgMilk)"  = `Feed Cost per Kg Milk ($)`
  ) %>% 
  dplyr::relocate(`Feed Cost ($/cow)`, .after = "IOFC Dry (\\$/Cow)") %>% 
  kableExtra::kbl(escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```


## {-}

<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Wisconsin-Madison </p>
<center>

```{r, warning = FALSE, echo = FALSE}

path_logo <- system.file("app/www", "uw_logo.png", package = "DairyPrintModel")

htmltools::img(
   src = knitr::image_uri(path_logo),
   style = "width:25px; height:40px;")
   
```
</center>
&nbsp;


