---
title: "**DairyPrint Model Report**"
output:
  html_document:
    theme:
      version: 4
params:
  total_co2e_q_emitted: 'NULL'
  co2eq_milk: 'NULL'
  methane_table: 'NULL'
  suma_table: 'NULL'
 
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 34px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 28px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}
</style>

***

This report represents ... Disclaimer?

***


## **1. Overall environmental outcomes** 

```{r, warning = FALSE, echo = FALSE}

params$suma_table

reactable::reactable(mtcars, pagination = FALSE, highlight = TRUE)

rnorm(1000000)

```


```{r, warning = FALSE, echo = FALSE}


```

## ** 2. Animal outcomes **

Just etsting something...

```{r, warning = FALSE, echo = FALSE}



```

## ** **

```{r, warning = FALSE, echo = FALSE}

reactable::reactable(params$methane_table, pagination = FALSE, highlight = TRUE)


```

## ** 3. **

```{r}


rnorm(1000000) %>% 
  hist()
echarts4r::e_chart(width = 1100, height = 550,
                         renderer = "svg") %>%
        echarts4r::e_list(list(
          tooltip = list(trigger = "item"),
          legend = list(top = "5%", left = "center"),
          series = list(
            list(
              name = "Access From",
              type = "pie",
              radius = c("40%", "70%"),
              avoidLabelOverlap = FALSE,
              itemStyle = list(
                borderRadius = 10,
                borderColor = "#fff",
                borderWidth = 2
              ),
              label = list(show = FALSE, position = "center"),
              emphasis = list(
                label = list(
                  show = TRUE,
                  fontSize = 40,
                  fontWeight = "bold"
                )
              ),
              labelLine = list(show = TRUE),
              data = list(
                list(value = 50, me = "Methane"),
                list(value = 20,     name  = "CO2"),
                list(value = 30,     name  = "N2O")
              )
            )
          )
        ))
```



</div>

&nbsp;
<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Wisconsin-Madison </p>
<center>
```{r, echo = FALSE}
 
htmltools::img(
   src = knitr::image_uri(here::here("inst/app/www/uw_logo.png")),
   style = "width:45px; height:45px;")
   
```
</center>
&nbsp;


