---
title: "**DairyPrint Model Report**"
output:
  html_document:
    theme:
      version: 4
params:
  total_co2e_q_emitted: 'NULL'
  co2eq_milk: 'NULL'
  methane_table: 'NULL'
  suma_table: 'NULL'
 
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 34px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 28px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}
</style>

***

This report represents ... Disclaimer?

***


## **1. Overall environmental outcomes** 

```{r, warning = FALSE, echo = FALSE}



```


```{r, warning = FALSE, echo = FALSE}

fig <- plotly::plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = round(params$co2eq_milk, 1),
  title = list(text = "CO2eq/kgMilk"),
  type = "indicator",
  mode = "gauge+number+delta",
  delta = list(reference = 1),
  gauge = list(
    axis = list(range = list(NULL, 2)),
    steps = list(
      list(range = c(0, 1), color = "lightgray"),
      list(range = c(1, 1.8), color = "orange")),
    threshold = list(
      line = list(color = "red", width = 6),
      thickness = 0.75,
      value = 1.8)),
  width = 400, height = 300) %>%
  plotly::config(displayModeBar = FALSE) %>%
  plotly::layout(showlegend = FALSE)

fig

```

## ** 2. Animal outcomes **

```{r, warning = FALSE, echo = FALSE}



```

## ** **

```{r, warning = FALSE, echo = FALSE}

reactable::reactable(params$methane_table, pagination = FALSE, highlight = TRUE)


```

## ** 3. **

```{r}


```



</div>

&nbsp;
<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Wisconsin-Madison </p>
<center>
```{r, echo = FALSE}
 
htmltools::img(
   src = knitr::image_uri(here::here("inst/app/www/uw_logo.png")),
   style = "width:45px; height:45px;")
   
```
</center>
&nbsp;


