---
title: "**DairyPrint Model Report**"
output:
  html_document:
    theme:
      version: 4
params:
  total_co2e_q_emitted: 'NULL'
  methane_table: 'NULL'
  suma_table: 'NULL'
 
  
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 34px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 28px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}
</style>

***

This report represents ... Disclaimer?

***


## **1. Overall environmental outcomes** 

```{r, warning = FALSE, echo = FALSE}

fluidRow(
summaryBox::summaryBox("Total Carbon Eq. (ton./year)", round(params$total_co2e_q_emitted / 1000, 1), width = 4, icon = "fa-solid fa-chart-line", style = "info"),
summaryBox::summaryBox("Carbon Eq. per kg Milk", round(params$suma_table, 1), width = 4, icon = "fa-solid fa-chart-line", style = "info")

)


```



## **This is just a test for report generation**

```{r, warning = FALSE, echo = FALSE}

fluidRow(
summaryBox::summaryBox("Methane Intensity", round(params$suma_table, 1), width = 4, icon = "fa-solid fa-chart-line", style = "info"),
summaryBox::summaryBox("Methane Intensity", round(params$suma_table, 1), width = 4, icon = "fa-solid fa-chart-line", style = "info"),
summaryBox::summaryBox("Methane Yield",     round(params$suma_table, 1), width = 4, icon = "fa-solid fa-chart-line", style = "info")

)

```



```{r, warning = FALSE, echo = FALSE}

reactable::reactable(params$methane_table, pagination = FALSE, highlight = TRUE)


```



