---
title: "**DairyPrint Model Report**"
output:
  html_document:
    theme:
      version: 4
params:
  total_co2e_q_emitted: 'NULL'
  co2eq_milk: 'NULL'
  methane_table: 'NULL'
  suma_table: 'NULL'
  animal_inputs: 'NULL'
  nh3_emissions: 'NULL'
  crop_inputs: 'NULL'
 
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 34px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 28px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 18px;
  color: #007582;
  
}
h4 { /* Header 4 */
  font-family: Helvetica;
  font-size: 14px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}
</style>

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

## **1. Farm Inputs:**

### **1.1 Herd Management**

```{r, warning = FALSE, echo = FALSE}
library(formattable)
#library(kableExtra)

kableExtra::kbl(params$animal_inputs, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = T, color = "white", background = "#007582")

```


### **1.2 Manure Management**

### **1.3 Crops and Purchased Feeds**

## **2. Farm Outcomes**




### This section will have three columns

<div class="col3">
**1** one  
**2** two  
**3** three  
**4** four  
**5** five  
**6** six  
**7** seven  
**8** eight  
**9** nine  
</div>


```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 4, fig.fullwidth=TRUE}

# barn <- params$nh3_emissions %>% 
#   dplyr::filter(year_day > 365) %>% 
#   ggplot2::ggplot( ggplot2::aes( x = year_day, y = barn_ch4_emissions_kg)) +
#   ggplot2::theme_bw() +
#   ggplot2::geom_point(col = "blue") +
#   ggplot2::geom_line(ggplot2::aes( x = year_day, y = barn_ch4_emissions_kg), col = "black") +
#   ggplot2::xlab("Year days") + ggplot2::ylab("Methane Emissions") + ggplot2::ggtitle("Barn")
# 
# storage <- params$nh3_emissions %>% 
#   dplyr::filter(year_day > 365) %>% 
#   ggplot2::ggplot( ggplot2::aes( x = year_day, y = storage_ch4_emissions_kg)) +
#   ggplot2::theme_bw() +
#   ggplot2::geom_point(col = "blue") +
#   ggplot2::geom_line(ggplot2::aes( x = year_day, y = storage_ch4_emissions_kg), col = "blue") +
#   ggplot2::xlab("Year days") + ggplot2::ylab("Methane Emissions") + ggplot2::ggtitle("Storage")
# 
# patchwork::wrap_plots(barn, storage, ncol = 2)

params$crop_inputs


```


### This section will have two columns

<div class="col2">
```{r}

methane_table <- params$methane_table %>% tibble::as_tibble()
methane_table$`Methane (%)` <- color_bar("lightgreen")(methane_table$`Methane (%)`)

kableExtra::kbl(methane_table, escape = FALSE) %>%
  kableExtra::kable_paper("hover", full_width = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582")

```
</div>


## **1. Overall environmental outcomes** 

## Results {.tabset}

### **Plots**

We show a scatter plot in this section.

```{r, fig.dim=c(5, 3)}
par(mar = c(4, 4, .5, .1))
plot(mpg ~ hp, data = mtcars, pch = 19)
```

### **Tables**

We show the data in this tab.

```{r, warning = FALSE, echo = FALSE}

params$suma_table


```

## {-}

### **Comments:**
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

Here are the comments




</div>

&nbsp;
<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Wisconsin-Madison </p>
<center>
```{r, echo = FALSE}
 
htmltools::img(
   src = knitr::image_uri(here::here("inst/app/www/uw_logo.png")),
   style = "width:45px; height:45px;")
   
```
</center>
&nbsp;


